Improving the portuguese hyphenation rules

### 2023-04-13 article/article.tex
compund word hyphenations

>>>>

Unfortunately, some specific hyphenation rules are not possible to be
implemented using the \TeX{} hyphenation algorithm. In German, for example,
there are no hyphens in compound words. Additionally, when words are hyphenated
some letters might also change. Furthermore, the spelling reform made changes,
making it necessary to create a different set of rules. For example, the German
word \emph{Schiffahrt} should be hyphenated as \emph{Schiff-fahrt}, preserving
the \emph{f}s from each word that make this compound. The hyphenation should
insert a \emph{f} that is not part of the written form. That was not a problem
for the old written form of the word: \emph{Schifffahrt}. Also, the old
hyphenating rules of German grammar stated the hyphenation \emph{Bäk-ker} for
the word \emph{Bäcker}, \emph{Zuk-ker} for the word \emph{Zucker} and
\emph{pak-ken} for the word \emph{packen}. Now those words are hyphenated as
\emph{Bä-cker}, \emph{Zu-cker} and \emph{pa-cken}, respectively. Some words
have also changed their hyphenation point after the spelling reform. For
example, \emph{Fen-ster} became \emph{Fens-ter}and \emph{mei-stens} became
\emph{meis-tens}. Some problems in compound word hyphenation in \TeX{} are
discussed in \cite{sojka1995a}.
